A hierarchical model to evaluate pest treatments from prevalence and intensity data

### 2023-09-04 Article.qmd

```{r dependencies, cache = FALSE, include = FALSE}
library(ggplot2);
library(tidyverse);
library(gridExtra);
library(rjags);
library(latex2exp);
library(grid);
library(dplyr);
library(tidyr);
library(tibble)
library(kableExtra)

source(file = "Files_for_code/Functions.R")

@@

```{r figure1, cache = FALSE, echo = FALSE, out.width="100%", fig.height = 3.8}
#| label: fig-one 
#| fig-cap: "Description of the dataset. **A** Number of observations according to the type of insecticide. **B** Examples of observed number of aphids averaged over the blocks (intensity) and number of infested beets out of ten (prevalence) averaged over the blocks, at different dates for two trials. Days post treatment is equal to the number of days between the observation date and the treatment. The colors represent the different treatments."
knitr::include_graphics("figures/fig1.png")
```

@@

```{r inference_example_real_data, cache = FALSE, eval = TRUE, results = 'hide'}
# The following code presents the inference on an extract fo the real 
# dataset, which includes both trials of figure 1B (2020 - B1A97 ; 2020 - 
# u1CwE). It is  a demo for the "50% Y / 50% Z" scenario and we set here the 
# number of adaptation and iteration to 2000 in order to reduce computation 
# time.

# Jags code for the model  #################################################
modelstringYZ = "
    model {

        # Likelyhood #####################################################
        for (i in 1:Q){
            Y[i] ~ dpois(N[i] * lb[i])
            Z[i] ~ dbinom(pi[i], N[i])

            log(lb[i]) = beta0[ID[i]] + gamma0[INSEC[i]] + (alpha1 + 
                         gamma1[INSEC[i]]) * TIME[i] + u[ST[i]] + epsi[i]

            pi[i] = 1 - exp(- lb[i])
            epsi[i] ~ dnorm(0, pi_eps)
        }

        for (j in 1:K){
            beta0[j] ~ dnorm(alpha0, tau0)
        }

        for (c in 1:M){
            u[c] ~ dnorm(0, invchi)
        }

        gamma0[1] = 0
        gamma1[1] = 0

        # Priors #########################################################
        for (s in 2:L){
            gamma0[s] ~ dnorm(0, 0.001)
            gamma1[s] ~ dnorm(0, 0.001)
        }

        alpha0 ~ dnorm(0, 0.001)
        alpha1 ~ dnorm(0, 0.001)
        sigma0 ~ dunif(0, 10)
        chi ~ dunif(0, 10)
        eta ~ dunif(0, 10)

        # Derived Quantities #############################################
        tau0 = pow(sigma0, -2)
        invchi = pow(chi, -2)
        pi_eps = pow(eta, -2)

        for (h in 2:L){
            for(t in 1 : T){
                Eff[h, t]  = (1 - exp(gamma0[h] + gamma1[h] * 
                             TIME_unique[t])) * 100
            }
        }  
    }
"

writeLines(modelstringYZ, con  =  "Files_for_code/modelYZ.txt")
############################################################################

# Inference example on the extract of the real dataset #####################
load(file = "Files_for_code/real_data_extract.Rdata")
data = real_data_extract %>% 
    mutate(tscaled = scale(DPT), st = paste(ID, Insecticide))

# Building scenarios -------------------------------------------------------
scenarioY = data %>% mutate(Z = NA)
scenarioYhalfZhalf = data %>% mutate(Y = ifelse(ID == "2020 - B1A97", Y, NA), 
                                     Z = ifelse(ID == "2020 - B1A97", NA, Z))
scenarioYhalf = data %>% filter(ID == "2020 - B1A97") %>% mutate(Z = NA)
scenarioZhalf = data %>% filter(ID == "2020 - u1CwE") %>% mutate(Y = NA)
# ---------------------------------------------------------------------------

data = scenarioYhalfZhalf

Y = data$Y;   Q = length(Y);   N = data$N;   Z = data$Z

ID = as.numeric(as.factor(as.character(data$ID)));   
INSEC = as.numeric(as.factor(as.character(data$Insecticide)));   
TIME = as.numeric(data$tscaled);   
ST = as.numeric(as.factor(as.character(data$st)));

K = length(unique(ID));   L = length(unique(INSEC));   
M = length(unique(ST));

df_TIME = suppressMessages(data %>% 
    group_by(DPT, tscaled) %>% 
    summarise(n = n()) %>% as.data.frame)

TIME_unique = approx(df_TIME$DPT, df_TIME$tscaled, xout = c(6, 12))$y;   
T = length(unique(TIME_unique))

data_jags = list(
              "Y" = Y, "Z" = Z, "Q" =  Q, "ID" = ID, "INSEC" = INSEC, 
              "TIME" = TIME, "ST" = ST, "K" = K, "L" = L, "M" = M, 
              "N" = N, "T" = T, "TIME_unique" = TIME_unique
            )

nadapt = 2000;   niter = 2000

model <- jags.model("Files_for_code/modelYZ.txt", data = data_jags, 
					n.chains = 2, n.adapt = nadapt)

samples <- coda.samples(model, 
                        variable.names = c("gamma0", "gamma1", "Eff"), 
                        n.iter = niter, thin = 10)
save(samples, file = "Files_for_code/Results/Real_data/samples.Rdata")
############################################################################
```

In practice, it is common that only $Y$ or $Z$ data are available in some of the trials. In this case, the resulting dataset includes observations of $Y$ in some trials and observations of $Z$ in others. The dataset may even include one type of observations only, either $Y$ or $Z$, in all trials. Here, we define four scenarios with contrasted levels of $Y$ and $Z$ availability in order to evaluate the consequences of using different types of datasets. We consider four datasets including trials with observations of $Y$, with observations of $Z$, or with both types of observation in different proportions (Table 2). The dataset "100% Y" includes Y data collected in the 32 trials. The dataset "50%Y" includes Y data collected in the 17 trials for which no Z observation is available. The dataset "50% $Z$" includes the Z data collected in the 15 trials for which Z observations are available. The dataset "50% $Y$ - 50% $Z$" includes $Y$ data collected in 17 trials and $Z$ data collected in the other 15 trials. The later dataset does include any trial reporting both $Y$ and $Z$ data.

@@

```{r simulations, cache = FALSE, eval = TRUE, results = 'hide'}
J = 4;   T = 3;   N = 10;   K = 4;

Block = c(1 : K);   Band = c(1 : J);   
Beet = c(1 : N);   DPT = seq(0, 12, length.out = T);

alpha0 = 0.5;   gamma0 = c(0, - 0.13, - 1.13, - 1.24);       
alpha1 = 0.16;   gamma1 = c(0, 0.24, - 0.14, - 0.15);
sig0 = 1.87;   chi = 0.27;   eta = 0.98

############################################################################

# Building scenarios #######################################################
# Scenarios "50% Y" and "50% Z" are obtained from scenarios "100% Y" and 
# "100% Z", respectively. For example "50% Y" scenario with 40 trials 
# corresponds to "100% Y" with 20 trials.

seed = 1;   I = 10
data = suppressMessages(simu_data(seed = seed, I = I))

scenarios = list(
    Y = data$dataYZ %>% mutate(Z = NA),
    Z = data$dataYZ %>% mutate(Y = NA),
    YhalfZhalf = data$dataYZ %>% mutate(Y = ifelse(ID <= (I / 2), NA, Y), 
                                        Z = ifelse(ID > (I / 2), NA, Z)),
    YhalfZ = data$dataYZ %>% mutate(Y = ifelse(ID <= (I / 2), NA, Y)),
    YZ = data$dataYZ,
    W = data$dataW
)
#############################################################################

# Inference #################################################################
nadapt = 2000;   niter = 2000

res_inf = NULL

# Inference YZ --------------------------------------------------------------
ID = as.numeric(as.factor(as.character(scenarios$Y$ID)));   
INSEC = as.numeric(as.factor(as.character(scenarios$Y$Insecticide)));   
TIME = as.numeric(scenarios$Y$tscaled);   
ST = as.numeric(as.factor(as.character(scenarios$Y$st)));

K = length(unique(ID));   
L = length(unique(INSEC));   
M = length(unique(ST))

TIME_unique = unique(scenarios$Y$tscaled)[2 : 3]  
T = length(unique(TIME_unique))

for(i in (1 : 5)){
    Y = scenarios[[i]]$Y;   Z = scenarios[[i]]$Z;   
    N = scenarios[[i]]$N;   Q = length(Y)

    data_jags = list(
                  "Y" = Y, "Z" = Z, "Q" =  Q, "ID" = ID, "INSEC" = INSEC, 
                  "TIME" = TIME, "ST" = ST, "K" = K, "L" = L, "M" = M, 
                  "N" = N, "T" = T, "TIME_unique" = TIME_unique
                )

    model <- jags.model("Files_for_code/modelYZ.txt", data = data_jags, 
						n.chains = 2, n.adapt = nadapt)

    samples <- coda.samples(model, 
                            variable.names = c("gamma0", "gamma1", "Eff"), 
                            n.iter = niter, thin = 10)

    bind = list(samples);   
    names(bind) = paste("samples", names(scenarios)[i], sep = "_")

    res_inf = res_inf %>% append(bind)
}

# Inference W ---------------------------------------------------------------
ID = as.numeric(as.factor(as.character(scenarios$W$ID)));   
INSEC = as.numeric(as.factor(as.character(scenarios$W$Insecticide)));   
TIME = as.numeric(scenarios$W$tscaled);   
ST = as.numeric(as.factor(as.character(scenarios$W$st)));
SBIT = as.numeric(as.factor(as.character(scenarios$W$sbit)))

K = length(unique(ID));   L = length(unique(INSEC));   
M = length(unique(ST));   X = length(unique(SBIT))

TIME_unique = unique(scenarios$W$tscaled)[2 : 3]  
T = length(unique(TIME_unique))

W = scenarios$W$W;   Q = length(W)

data_jags = list(
             "W" = W, "Q" =  Q, "ID" = ID, "INSEC" = INSEC, 
             "TIME" = TIME, "ST" = ST,  "SBIT" = SBIT, "K" = K, "L" = L, 
             "M" = M, "X" = X, "T" = T, "TIME_unique" = TIME_unique
            )

model <- jags.model("Files_for_code/modelW.txt", data = data_jags, 
					n.chains = 2, n.adapt = nadapt)

samples <- coda.samples(model, 
                        variable.names = c("gamma0", "gamma1", "Eff"), 
                        n.iter = niter, thin = 10)

res_inf = res_inf %>% append(list("samples_W" = samples))
############################################################################

# Formatting results #######################################################
t = scenarios$Y$tscaled %>% unique
Eff_6_true = (1 - exp(gamma0[2 : J] + gamma1[2 : J] * t[2])) * 100
Eff_12_true = (1 - exp(gamma0[2 : J] + gamma1[2 : J] * t[3])) * 100
truth = c(Eff_6_true, Eff_12_true, gamma0[2 : J], gamma1[2 : J])

n_scenarios = length(scenarios)

esti = lapply(
         res_inf, function(x) summary(x)$statistics %>% as.data.frame %>% 
                    rownames_to_column %>% 
                    filter(!(grepl("gamma", rowname) & Mean == 0)) %>% 
                    select(Mean) %>% as.matrix %>% as.vector
       )

b_inf = lapply(
          res_inf, function(x) summary(x)$quantiles %>% as.data.frame %>% 
                    rownames_to_column %>% 
                    filter(!(grepl("gamma", rowname) & `2.5%` == 0)) %>% 
                    select(`2.5%`) %>% as.matrix %>% as.vector
        )

b_sup = lapply(
          res_inf, function(x) summary(x)$quantiles %>% as.data.frame %>% 
                    rownames_to_column %>% 
                    filter(!(grepl("gamma", rowname) & `2.5%` == 0)) %>% 
                    select(`97.5%`) %>% as.matrix %>% as.vector
        )

parameters = summary(res_inf[[1]])$statistics %>% as.data.frame %>% 
                    rownames_to_column %>% 
                    filter(!(grepl("gamma", rowname) & Mean == 0)) %>% 
                    select(rowname) %>% as.matrix %>% as.vector

res = do.call(rbind, 
              lapply(c(1 : n_scenarios), 
                 function(x) 
                    data.frame(Truth = truth, Scenario = names(scenarios)[x], 
                               I = I, seed = seed, 
                               value = esti[[x]], parameters = parameters, 
                               b_inf = b_inf[[x]], b_sup = b_sup[[x]]
                    )
              )
      )
############################################################################

# save(res, file = paste0("res.I.", I, ".seed.", seed, ".Rdata"))
```

@@

```{r load_res_real_data, cache = FALSE, echo = FALSE}
load(file = "Files_for_code/Results/Real_data/res.Y.nadapt.150000.niter.3e+05.Rdata");   resY = res
load(file = "Files_for_code/Results/Real_data/res.YhalfZhalf.nadapt.150000.niter.3e+05.Rdata");   resYZ = res
load(file = "Files_for_code/Results/Real_data/res.Yhalf.nadapt.150000.niter.3e+05.Rdata");   resYhalf = res
load(file = "Files_for_code/Results/Real_data/res.Zhalf.nadapt.150000.niter.3e+05.Rdata");   resZhalf = res
```

@@

```{r figure2, cache = FALSE, out.width="100%", fig.height = 7, echo = FALSE}
#| label: fig-two
#| fig-cap: "Model convergence - Markov chain for the model parameters and treatment efficacies, in the scenarios '50% Y' (**A**),  '50% Y / 50% Z' (**B**), '100% Y' (**C**) and '50% Z' (**D**). The x-axis presents the iteration number and the y-axis presents the sampled value."

@@

fig2A = suppressMessages(f_plot_chains(resYhalf, nrow = nrow) + ylab("Sampled value") + scale_x_continuous(breaks = c(0, 1.5e4, 3e4))) + xlab("") +
	scale_y_continuous(n.breaks = nbreaks) + theme(strip.text = element_text(size = strip_size))
my_g2A <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("A", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

fig2B = suppressMessages(f_plot_chains(resYZ, nrow = nrow) + ylab("Sampled value") + scale_x_continuous(breaks = c(0, 1.5e4, 3e4))) + xlab("") +
	scale_y_continuous(n.breaks = nbreaks) + theme(strip.text = element_text(size = strip_size))
my_g2B <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("B", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

fig2C = suppressMessages(f_plot_chains(resY, nrow = nrow) + ylab("Sampled value") + scale_x_continuous(breaks = c(0, 1.5e4, 3e4))) + xlab("") +
	scale_y_continuous(n.breaks = nbreaks) + theme(strip.text = element_text(size = strip_size))
my_g2C <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("C", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

fig2D = suppressMessages(f_plot_chains(resZhalf, nrow = nrow) + ylab("Sampled value") + scale_x_continuous(breaks = c(0, 1.5e4, 3e4))) +
	scale_y_continuous(n.breaks = nbreaks) + theme(strip.text = element_text(size = strip_size), axis.title.x = element_text(margin = margin(t = 5)))
my_g2D <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("D", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

@@

```{r figure3, cache = FALSE, out.width="100%", fig.height = 7, echo = FALSE}
#| label: fig-three
#| fig-cap: "Model convergence - Gelman-Rubin statistics for the parameters of the model (@eq-model_W - @eq-model_Z) and for treatment efficacies (@eq-Efficacy), according to the scenarios 50% Y (**A**),  50% Y / 50% Z (**B**), 100% Y (**C**) and 50% Z (**D**). The x-axis presents the iteration number and the y-axis presents the Gelman-Rubin statistic."

@@

```{r figure4, cache = FALSE, echo=FALSE, out.width = "100%", fig.height = 2.6}
#| label: fig-four
#| fig-cap: "Estimated treatment efficacies after 6 days (**A**) and after 12 days (**B**), with their credibility intervals. Colors correspond to the different scenarios."

@@

```{r table5}
#|echo: false
cbind(df_len6, df_len12 %>% select(- Data, - Insecticide)) %>% 
  kbl(booktabs = TRUE, caption = "Differences in the sizes of the 95 credibility intervals (CI) of the estimated treatment efficacies for the scenarios 50 Y / 50 Z, 50 Z and 100 Y, compared to 50 Y. The difference is given in percentage. A positive (negative) value indicates an increase (decrease) of the credibility interval size. The third column indicates differences for the efficacy at 6 days after pesticide spray, and the fourth column indicates the difference for the efficacy at 12 days.") %>% 
  kable_styling()
```

@@

```{r load_res_simulations, cache = FALSE, echo = FALSE}
load(file = "Files_for_code/Results/Simulations/df_col_simu.Rdata")
load(file = "Files_for_code/Results/Simulations/res_simu_sigma_1.87.Rdata")

@@

```{r table6}
#|echo: false

@@

```{r figure5, cache = FALSE, out.width="100%", fig.height = 2.5, echo = FALSE}
#| label: fig-five
#| fig-cap: "Values of the $E_{\\gamma}$ (@eq-E_gamma) (**A**), $E_{Ef_6}$ (@eq-E_efficacy) (**B**) and $E_{Ef_{12}}$ (@eq-E_efficacy) (**C**) mean absolute error criteria for the '50% Z', '50% Y' and '50% Y / 50% Z' scenarios. The x-axis presents the number of trials and the y-axis presents the mean absolute error, averaged over the 974 simulated datasets. Different colors correspond to different scenarios."

@@

```{r figure6, cache = FALSE, out.width="100%", fig.height = 3, echo = FALSE}
#| label: fig-six
#| fig-cap: "Comparison of proportion cases where the best treatment is correctly identified in the '50% Z', '50% Y' and '50% Y / 50% Z' scenarios. The x-axis represents the number of trials and the y-axis represents the percentage of cases where the best treatment has been correctly identified at 6 days (A) and 12 days (B), over the 974 simulated datasets. Different colors correspond to different scenarios."

@@

```{r figure7, cache = FALSE, out.width="100%", fig.height = 2.5, echo = FALSE}
#| label: fig-seven
#| fig-cap: "Values of $E_{\\gamma}$ (@eq-E_gamma) (**A**), $E_{Ef_6}$ (@eq-E_efficacy) (**B**) and $E_{Ef_{12}}$ (@eq-E_efficacy) (**C**) for the '100% Z', '50% Y', '100% Z / 50% Y' and '50% Y / 50% Z' scenarios. The x-axis presents the number of trials and the y-axis presents the absolute error averaged over the 974 simulated datasets. Different colors correspond to different scenarios."

@@

```{r table7}
#|echo: false

@@

load(file = "Files_for_code/Results/Simulations/res_simu_q3_1.Rdata");   load(file = "Files_for_code/Results/Simulations/res_simu_q3_2.Rdata")

>>>>

```{r dependencies, cache = FALSE, include = FALSE}
library(ggplot2);
library(tidyverse);
library(gridExtra);
library(rjags);
library(latex2exp);
library(grid);
library(dplyr);
library(tidyr);
library(tibble)
library(kableExtra)
library(coda)

@@

```{r, fig.width=12, fig.height=14}
#| echo: false
#| label: fig-one 
#| fig-cap: "Description of the dataset. **A** Number of observations according to the type of insecticide. **B** Examples of observed number of aphids averaged over the blocks (intensity) and number of infested beets out of ten (prevalence) averaged over the blocks, at different dates for two trials. Days post treatment is equal to the number of days between the observation date and the treatment. The colors represent the different treatments."

data_figure_1A = readRDS(file = "data/data_figure_1A.rds")
data_figure_1B = readRDS(file = "data/data_figure_1B.rds")

rectangle_fig1A <- grobTree(rectGrob(gp = gpar(fill = "#e9e9e9")), textGrob("A", x = 0.5, hjust = 0.5, gp = gpar(cex = 2.5, fontface = "bold")))

fig1A = ggplot(data_figure_1A) + 
    geom_bar(aes(x = Insecticide, y = n, fill = Insecticide), stat = "Identity") + 
    xlab("Insecticide") + 
    ylab("Number of observations") +
    scale_fill_manual(values = c('#df626c', '#893f3d', '#ff842e', '#188038')) + 
    scale_x_discrete(limits = c("Untreated", "Mavrik Jet", "Movento", "Teppeki")) + 
    theme(legend.position = "none", 
          axis.title.x = element_text(margin = margin(b = 50, t = 20), size = 18),
          axis.title.y = element_text(size = 18, margin = margin(r = 20)),
          axis.text = element_text(size = 16))

rectangle_fig1B <- grobTree(rectGrob(gp = gpar(fill = "#e9e9e9")), textGrob("B", x = 0.5, hjust = 0.5, gp = gpar(cex = 2.5, fontface = "bold")))

fig1B_aphid_intensity = ggplot(data_figure_1B) + 
    geom_point(aes(x = DPT, y = Ymean, col = Insecticide), size = 2.5) + 
    geom_line(aes(x = DPT, y = Ymean, col = Insecticide), size = 0.2) +
    scale_color_manual(values = c('#893f3d', '#ff842e', '#188038')) + 
    facet_wrap(~ ID, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    xlab("") + 
    ylab("Number of aphids") +
    theme(plot.margin = margin(t = 40, r = 40, b = 0, l = 10), 
          axis.title.x = element_text(size = 18),
          axis.title.y = element_text(size = 18, margin = margin(r = 20)),
          axis.text = element_text(size = 16),
          strip.text = element_text(size = 20),
          legend.title = element_text(size = 18),
          legend.text = element_text(size = 18))

fig1B_aphid_prevalence = ggplot(data_figure_1B) + geom_point(aes(x = DPT, y = Zmean, col = Insecticide), size = 2.5) + 
    geom_line(aes(x = DPT, y = Zmean, col = Insecticide), size = 0.2) +
    scale_color_manual(values = c('#893f3d', '#ff842e', '#188038')) + 
    facet_wrap(~ ID, ncol = 2, scales = "free_x") + theme(legend.position = "none") + 
    xlab("Days post treatment") + 
    ylab("Number of infested beets") +
    theme(panel.spacing = unit(1, "cm")) +
    theme(plot.margin = margin(t = 0, r = 40, b = 0, l = 10), 
          axis.title.y = element_text(size = 18, margin = margin(r = 20)),
          axis.text = element_text(size = 16),
          axis.title.x = element_text(margin = margin(b = 20, t = 20), size = 18),
          strip.text = element_text(size = 20))

legend <- cowplot::get_legend(fig1B_aphid_intensity)

do.call("grid.arrange", 
        c(list(rectangle_fig1A, 
               fig1A + theme(plot.margin = margin(t = 30, r = 20)), 
               rectangle_fig1B, 
               fig1B_aphid_intensity + theme(legend.position = "none"),
               fig1B_aphid_prevalence), list(legend), list(ncol = 1, 
             layout_matrix = rbind(c(1), c(2), c(3), c(4), c(5), c(6)), heights = c(0.12, 1.2, 0.12, 1, 1, 0.12))))
```

@@

::: {.callout-note}
The following code presents the inference on an extract fo the real 
dataset, which includes both trials of figure 1B (2020 - B1A97 ; 2020 - 
u1CwE). It is  a demo for the "50% Y / 50% Z" scenario and we set here the 
number of adaptation and iteration to 2000 in order to reduce computation 
time.
:::

```{r inference_example_real_data, cache = TRUE, results = 'hide'}
#| echo: true
#| eval: false
#| file: scripts/inference_example_real_data.R
```

\
In practice, it is common that only $Y$ or $Z$ data are available in some of the trials. In this case, the resulting dataset includes observations of $Y$ in some trials and observations of $Z$ in others. The dataset may even include one type of observations only, either $Y$ or $Z$, in all trials. Here, we define four scenarios with contrasted levels of $Y$ and $Z$ availability in order to evaluate the consequences of using different types of datasets. We consider four datasets including trials with observations of $Y$, with observations of $Z$, or with both types of observation in different proportions (Table 2). The dataset "100% Y" includes Y data collected in the 32 trials. The dataset "50%Y" includes Y data collected in the 17 trials for which no Z observation is available. The dataset "50% $Z$" includes the Z data collected in the 15 trials for which Z observations are available. The dataset "50% $Y$ - 50% $Z$" includes $Y$ data collected in 17 trials and $Z$ data collected in the other 15 trials. The later dataset does include any trial reporting both $Y$ and $Z$ data.

@@

```{r simulations, results = 'hide'}
#| echo: true
#| eval: false
#| file: scripts/simulations.R
```

@@

```{r load_res_real_data, cache = FALSE, echo = FALSE}
resY = readRDS(file = "Files_for_code/Results/Real_data/res.Y.nadapt.150000.niter.3e+05.rds")
resYZ = readRDS(file = "Files_for_code/Results/Real_data/res.YhalfZhalf.nadapt.150000.niter.3e+05.rds") 
resYhalf = readRDS(file = "Files_for_code/Results/Real_data/res.Yhalf.nadapt.150000.niter.3e+05.rds")  
resZhalf = readRDS(file = "Files_for_code/Results/Real_data/res.Zhalf.nadapt.150000.niter.3e+05.rds") 
```

@@

```{r figure2, cache = TRUE, out.width="100%", fig.height = 7, echo = FALSE}
#| label: fig-two
#| fig-cap: "Model convergence - Markov chain for the model parameters and treatment efficacies, in the scenarios '50% Y' (**A**),  '50% Y / 50% Z' (**B**), '100% Y' (**C**) and '50% Z' (**D**). The x-axis presents the iteration number and the y-axis presents the sampled value."

source(file = "functions/plot_chains.R")

@@

fig2A = suppressMessages(plot_chains(resYhalf, nrow = nrow) + ylab("Sampled value") + scale_x_continuous(breaks = c(0, 1.5e4, 3e4))) + xlab("") +
	scale_y_continuous(n.breaks = nbreaks) + theme(strip.text = element_text(size = strip_size))
my_g2A <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("A", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

fig2B = suppressMessages(plot_chains(resYZ, nrow = nrow) + ylab("Sampled value") + scale_x_continuous(breaks = c(0, 1.5e4, 3e4))) + xlab("") +
	scale_y_continuous(n.breaks = nbreaks) + theme(strip.text = element_text(size = strip_size))
my_g2B <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("B", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

fig2C = suppressMessages(plot_chains(resY, nrow = nrow) + ylab("Sampled value") + scale_x_continuous(breaks = c(0, 1.5e4, 3e4))) + xlab("") +
	scale_y_continuous(n.breaks = nbreaks) + theme(strip.text = element_text(size = strip_size))
my_g2C <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("C", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

fig2D = suppressMessages(plot_chains(resZhalf, nrow = nrow) + ylab("Sampled value") + scale_x_continuous(breaks = c(0, 1.5e4, 3e4))) +
	scale_y_continuous(n.breaks = nbreaks) + theme(strip.text = element_text(size = strip_size), axis.title.x = element_text(margin = margin(t = 5)))
my_g2D <- grobTree(rectGrob(gp = gpar(fill = col_background)), textGrob("D", x = 0.5, hjust = 0.5, gp = gpar(col = col_text, cex = cex, fontface = "bold")))

@@

```{r figure3, cache = TRUE, out.width="100%", fig.height = 7, echo = FALSE}
#| label: fig-three
#| fig-cap: "Model convergence - Gelman-Rubin statistics for the parameters of the model (@eq-model_W - @eq-model_Z) and for treatment efficacies (@eq-Efficacy), according to the scenarios 50% Y (**A**),  50% Y / 50% Z (**B**), 100% Y (**C**) and 50% Z (**D**). The x-axis presents the iteration number and the y-axis presents the Gelman-Rubin statistic."

source(file = "functions/gelman.plot2.R")

@@

```{r figure4, cache = TRUE, echo=FALSE, out.width = "100%", fig.height = 2.6}
#| label: fig-four
#| fig-cap: "Estimated treatment efficacies after 6 days (**A**) and after 12 days (**B**), with their credibility intervals. Colors correspond to the different scenarios."

@@

```{r table5, cache = TRUE}
#|echo: false
cbind(df_len6, df_len12 %>% select(- Data, - Insecticide)) %>% 
  kbl(booktabs = TRUE, caption = "Differences in the sizes of the 95 credibility intervals (CI) of the estimated treatment efficacies for the scenarios 50 Y / 50 Z, 50 Z and 100 Y, compared to 50 Y. The difference is given in percentage. A positive (negative) value indicates an increase (decrease) of the credibility interval size. The third column indicates differences for the efficacy at 6 days after pesticide spray, and the fourth column indicates the difference for the efficacy at 12 days.") %>% 
  kable_styling()
```

@@

```{r load_res_simulations, cache = FALSE, echo = FALSE}
df_col_simu = readRDS(file = "Files_for_code/Results/Simulations/df_col_simu.rds")
res_simu_sigma_1.87 = readRDS(file = "Files_for_code/Results/Simulations/res_simu_sigma_1.87.rds")

@@

```{r table6, cache = TRUE}
#|echo: false

@@

```{r figure5, cache = TRUE, out.width="100%", fig.height = 2.5, echo = FALSE}
#| label: fig-five
#| fig-cap: "Values of the $E_{\\gamma}$ (@eq-E_gamma) (**A**), $E_{Ef_6}$ (@eq-E_efficacy) (**B**) and $E_{Ef_{12}}$ (@eq-E_efficacy) (**C**) mean absolute error criteria for the '50% Z', '50% Y' and '50% Y / 50% Z' scenarios. The x-axis presents the number of trials and the y-axis presents the mean absolute error, averaged over the 974 simulated datasets. Different colors correspond to different scenarios."

@@

```{r figure6, cache = TRUE, out.width="100%", fig.height = 3, echo = FALSE}
#| label: fig-six
#| fig-cap: "Comparison of proportion cases where the best treatment is correctly identified in the '50% Z', '50% Y' and '50% Y / 50% Z' scenarios. The x-axis represents the number of trials and the y-axis represents the percentage of cases where the best treatment has been correctly identified at 6 days (A) and 12 days (B), over the 974 simulated datasets. Different colors correspond to different scenarios."

@@

```{r figure7, cache = TRUE, out.width="100%", fig.height = 2.5, echo = FALSE}
#| label: fig-seven
#| fig-cap: "Values of $E_{\\gamma}$ (@eq-E_gamma) (**A**), $E_{Ef_6}$ (@eq-E_efficacy) (**B**) and $E_{Ef_{12}}$ (@eq-E_efficacy) (**C**) for the '100% Z', '50% Y', '100% Z / 50% Y' and '50% Y / 50% Z' scenarios. The x-axis presents the number of trials and the y-axis presents the absolute error averaged over the 974 simulated datasets. Different colors correspond to different scenarios."

@@

```{r table7, cache = TRUE}
#|echo: false

@@

res_simu_q3_1 = readRDS(file = "Files_for_code/Results/Simulations/res_simu_q3_1.rds");   
res_simu_q3_2 = readRDS(file = "Files_for_code/Results/Simulations/res_simu_q3_2.rds")
